Discovery of s-process stars in the LAMOST survey

### 2018-02-05 article/ms.tex
drafty

For the remainder of this paper we restrict our analysis to the 257 classical `Barium stars' stars that show enhancement in both barium and strontium. While the 49 or 661 stars with only barium or strontium enhancements (respectively) may also be bonafide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a gold sample of Barium stars. Nevertheless, this sample still constitutes the largest collection of Barium stars ever discovered.\todo{\citet{decastro2016} merges all previously known Barium stars candidates into a confirmed Barium stellar sample cite the next biggest one or two samples}

@@

We conducted the largest ever search for s-process enhanced stars using the LAMOST second data release. From 454,180 giant stars, we identify 967 s-process candidates including: 257 stars with significant enhancements in barium and strontium (so-called `Barium stars'); 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement. This sample size is double the total number of Barium stars known, and represents the largest sample of s-process enhanced stars to date. Nearly all of our Barium candidates are consistent with being disk stars.

>>>>

For the remainder of this paper we restrict our analysis to the 257 classical `Barium stars' stars that show enhancement in both barium and strontium. While the 49 or 661 stars with only barium or strontium enhancements (respectively) may also be bonafide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a gold sample of Barium stars. Nevertheless, this sample still constitutes the largest collection of Barium stars ever discovered; the stellar sample given in \citet{decastro2016} constitutes the next largest Barium star candidate list.

@@

We conducted the largest ever search for s-process enhanced stars using the LAMOST second data release. From 454,180 giant stars, we identify 967 s-process candidates including: 257 stars with significant enhancements in barium and strontium (so-called `Barium stars'); 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement. This sample size is greatest total number of Barium stars known, and represents the largest sample of s-process enhanced stars to date. Nearly all of our Barium candidates are consistent with being disk stars.
